\normalfont{A bird's-eye view on the habitability of exoplanets via statistical learning techniques}

### 2020-09-22 Manuscript/Manuscript.tex
pub

Such relation establish an interval for the distance $r$ where the stellar radiation is not too hot so that the water is the gas phase, and not to low so only the solid state phase is allowed. In the literature this interval is usually called habitable-zone \cite{kasting1993habitable}. However this represents a too simplified model since no atmospheric effect is taken in to account: indeed the surface temperature is also influenced by the greenhouse gases that allows to the host radiation to enter inside the planet but limits its escape \cite{seager2013exoplanet,forget2014possible}. Basically this is due to the fact that the greenhouse molecules (CO$_{2}$,vapour, methane...) are excited by the infra-red radiation produced by the planet and remit it in all directions. As consequence the radiation that is emitted by the planet is reduced, and so the temperature is increased. It is worth nothing that in principle the greenhouse is not negative since it allows to the planet to keep part of the heath received from the host star. However this can be a problem if the effect so large that the temperature of the planet abruptly increase: this was probably the fate of Venus that lost his oceans \cite{way2016venus,luger2015extreme,seager2013exoplanet}.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Pic/Planets_habitability_Seager.png}
\caption{Seager representation of planet habitability as function of star type (that determinates the stellar activity) and planet distance. Image taken from \cite{seager2013exoplanet}}
\label{Planets_habitability_Seager}
\end{center}
\end{figure}

>>>>

Such relation establish an interval for the distance $r$ where the stellar radiation is not too hot so that the water is the gas phase, and not to low so only the solid state phase is allowed. In the literature this interval is usually called habitable-zone \cite{kasting1993habitable}. However this represents a too simplified model since no atmospheric effect is taken in to account: indeed the surface temperature is also influenced by the greenhouse gases that allows to the host radiation to enter inside the planet but limits its escape \cite{seager2013exoplanet,forget2014possible}. Basically this is due to the fact that the greenhouse molecules (CO$_{2}$,vapour, methane...) are excited by the infra-red radiation produced by the planet and remit it in all directions. As consequence the radiation that is emitted by the planet is reduced, and so the temperature is increased. It is worth nothing that in principle the greenhouse is not negative since it allows to the planet to keep part of the heath received from the host star. However this can be a problem if the effect is so large that the temperature of the planet abruptly increase: this was probably the fate of Venus that lost his oceans \cite{way2016venus,luger2015extreme,seager2013exoplanet}. As further requirement for the habitability is that the planet is rocky: so planets such as Jupiter or Saturn have to be excluded.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Pic/Planets_habitability_Seager.png}
\caption{Seager representation of planet habitability as function of star type (that determinates the stellar activity) planet distance and its atmosphere. Image taken from \cite{seager2013exoplanet}}
\label{Planets_habitability_Seager}
\end{center}
\end{figure}
